---
title: "bootstrapping"
author: "Ziqi Zhou"
date: "11/14/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
library(tidyverse)
library(p8105.datasets)

library(patchwork)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
set.seed(1)
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```


```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```

Fit two models
```{r}
sim_df_const %>% 
  lm(y ~x, data = . ) %>% 
  broom::tidy()

sim_df_nonconst %>% 
  lm(y ~x, data = . ) %>% 
  broom::tidy()
```
The R here the outcome is wrong. in the sim_df_nonconst std.error.
se is not correct here. though other things might be true.
Because of the assumption might be not true but we analysed use those assumption. 

##Check in echo360.

## how can I bootstrap

Write a function to draw a bootstrap sample based on a dataframe.
```{r}
sim_df_nonconst %>% 
  sample_frac(size = 1, replace = TRUE) %>%  #This is a wrapper around sample.int() to make it easy to 
  arrange(x)

```

```{r}
boot_sample = function(df){
  sample_frac(df,size = 1, replace = TRUE)
}
```

```{r}
boot_sample(df = sim_df_nonconst) %>% 
  ggplot(aes(x = x,y = y)) + 
  geom_point()
```

organize the dataframe.]
keeping track all the different boot_strap sample

```{r}
boot_straps = 
  tibble(
    strap_num = 1:1000,
    strap_sample = rerun(1000, boot_sample(df = sim_df_nonconst))
  ) 
```
do some kind of analysis
what the slope looks like? slope distribution?

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y~x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap_sample,-models) %>% 
  unnest(results)


```
summarize these results

```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))
```


##Try the modelr package.
The difference is in the begining how the sample generated?...?
```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(1000) %>% 
  mutate(
    models = map(strap, ~lm(y~x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap,-models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))

```



```{r}

```

## Revisit airbnb data.
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```


```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point() 
```
However this is not constant and so many outliners.

What is the distrib of the slope.

Re-use the stuff we just did
```{r}
nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(price ~ stars+ room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()
  
```

It is skew.




