---
title: "Cross Validation"
author: "Ziqi Zhou"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
library(tidyverse)
library(modelr)
library(mgcv)


options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

generate a dataset

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()
```

Training and testing

```{r}
training_df = sample_n(nonlin_df,80)
sample_frac(nonlin_df,0.8)  # also workd as the last code.
test_df = anti_join(nonlin_df, training_df, by = "id")

ggplot(training_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```
##??why no red points??

Fit three models of varying goodness.

```{r}
linear_mod = lm(y~x, data = training_df)
smooth_mod = mgcv::gam(y ~ s(x), data = training_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = training_df)
```


```{r}
training_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```



```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

which one is better for  ???????


always choose fit the test dataset better model.


# DO this all using modelr

preforms the training / testing split multiple times, a stores the datasets using list columns.
```{r}
cv_df =  
  crossv_mc(nonlin_df, 100)  # n(100)  is Number of test-training pairs to generate (an integer).
# nest data 

```
one note about resample

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as.tibble()
```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```
try fitting the linear model to all of these...

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_models = map(train, ~ lm(y ~ x, data = .x)),
    smooth_models = map(train, ~ gam(y ~ s(x), data = .x)),
    wiggly_models  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x)),
    
    rmse_lin = map2(.x = linear_models, .y = test, ~rmse(.x, .y)),
    rmse_smo = map2(.x = smooth_models, .y = test, ~rmse(.x, .y)),
    rmse_wig = map2(.x = wiggly_models, .y = test, ~rmse(.x, .y))
  ) 
```

compare different models
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>%   # put them in order
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


we goona choose smooth models


```{r}

```



